---
title: "Untitled"
author: "untilted"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

\newpage
```{r}
# Input the Fleming and Harrington Count Data (fhcnt) and name the covariates
fhcnt = read.table("https://biostatcenter.gwu.edu/sites/biostatcenter.gwu.edu/files/Lachin%20Files/fhcnt.txt",header=F)
names(fhcnt)=c("id","z1","z2","z3","z4","z5","z6","z7","z8","z9","nevents","futime")
```

# a)
```{r}
model <- glm(nevents~as.factor(z1)+as.factor(z2)+z3+z4+z5+as.factor(z6)+as.factor(z7)+as.factor(z8)+as.factor(z9)+offset(log(futime)),family = poisson(link = "log"),data = fhcnt)

summary(model)
```
# b)

```{r}
rd <- residuals.glm(model,"deviance")
fv <- model$fitted.values
plot(fv,rd,xlab="fitted value",ylab="deviance residual",main="scatterplot")
abline(h=2)
abline(h=-2)
```
We can see the there are some points lies above the two lines, thus the model is not fitted.

```{r}
qqnorm(rd)
abline(a=0,b=1)
```

We can see that in the middle of the graph, points are not lie along with the 
line, thus the model is not fitted

# c)
The estimated for treatment group is 1.156140
```{r}
exp(1.156140)
```
Thus the relative rate is 3.177644 = $\frac{\lambda_2}{\lambda_1}$ which $\lambda_2$ 
represent take placebo and $\lambda_1$ represent take interferon. Thus $\lambda_2 > \lambda_1$,
take interferon actually decrease the rate.
Thus treatment with interferon effective in reducing serious infections among children with CGD

```{r}
LOG_CI = 1.156140 + c(-1,1)*1.96*0.277853
exp(LOG_CI)
```
95% confidence interval of relative rate is [1.843283 ,5.477955]

\newpage

# d)
```{r}
x = as.matrix(c(0,0,0,0,0,0,0,0,0,0,1,-1),ncol=1)
v = summary(model)$cov.unscaled
se<-sqrt(t(x) %*% v %*% x)
mle = -0.955742-(-0.788223)
CI <- mle + c(-1,1)*1.96*se[1]
exp(CI)
```

Thus the 95% Confidence Interval of relative rate is [0.2761451 2.5903447]

# e)

$\hat\mu=\lambda \times t=exp(log(\hat\lambda)+log(t)$

$log(\hat\lambda) = x^T\hat\beta$

```{r}
beta = c(-5.348270,1.156140,0.754567,-0.083938,0.007649,0.010345,-1.958265,0.668546,
         -0.856499,-0.110733,-0.955742,-0.788223)

x = c(1,0,0,12,142,34,0,1,0,1,0,0)
log_hat = sum(beta*x)
mu = exp(log_hat+log(365.25))
mu
```
Estimated number of infections are 4.668123

# f)

The purpose of this study was to find the different variables that would influence
the results of a serious infections among children with chronic granulotomous disease.

The treatment group: interferon versus placebo (Odds Ratio(OR) = 3.18) and 
Inheritance pattern: X-linked  versus autosomal recessive (OR=2.127) were associated
with increased odds the response

Age (OR=0.919),  Corticosteroid use on entry: yesversus no(OR=0.1411) 
Gender: male  versus female (OR=0.4246) and Type of hospital: Amsterdam (OR = 0.3845)
were associated with decreased odds the response
```{r}
# Characteristics siginificantly associated with increased odds of response
exp(model$coeff)[model$coeff>0 & summary(model)$coeff[,4]<0.05]

# Characteristics siginificantly associated with decreased odds of response
exp(model$coeff)[model$coeff<0 & summary(model)$coeff[,4]<0.05]
```

